---
title: 'rROMA Docker image'
author: '[Luca Albergante](mailto:luca.albergante@gmail.com)'
date: 'May 2017'
output:
  md_document:
    toc: yes
    toc_depth: 2
---

# Description

This repository contains multiple descriptions of different interdependent dockers:

* `sysbiocurie/rBase` is based on `rocker/rstudio`and contains all the packages needed to run [rRoma](https://github.com/sysbio-curie/rRoma) and [rRomaDash](https://github.com/sysbio-curie/rRomaDash)

* `sysbiocurie/rRoma` is based on `sysbiocurie/rBase` and contains the stable version of [rRoma](https://github.com/sysbio-curie/rRoma), [rRomaDash](https://github.com/sysbio-curie/rRomaDash), and [RNaviCell](https://github.com/sysbio-curie/RNaviCell)

* `sysbiocurie/rRomaDevel` is based on `sysbiocurie/rbase` and contains the developer version of [rRoma](https://github.com/Albluca/rRoma), [rRomaDash](https://github.com/Albluca/rRomaDash), and the stable version of [RNaviCell](https://github.com/sysbio-curie/RNaviCell)

# Usage

To use the rRoma docker image, it is necessary, after installing [Docker](https://www.docker.com), to run the following command:

```{r, engine='bash', eval=FALSE}
docker pull sysbiocurie/rroma
```

After installation, the image can be started with the command

```{r, engine='bash', eval=FALSE}
docker run -p 8787:8787 sysbiocurie/rroma
```

At this point, the RStudio web interface containing rRoma will be availabe, in Unix-like systems, at the address [http://localhost:8787](http://localhost:8787). It is then possible to access the interface by using "rstudio" as the username and password.

On windows, it may be necessary to replace localhost with the address of the machine. If any problem is encountered see the instruction [here](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image).

After starting the interface, it is possible to write r code as in the desktop version of RStudio.
